Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex

In \cref{sec:image} in the main paper, we included experiments on image data sets. For the image-based classification experiments, we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
For the neural network training, we used the same set-up as in \cite{immer2021improving},
training the neural network using Adam for $500$ epochs with a batch size of $512$.
The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
and we ran each experiment for $5$ seeds.
The MNIST experiments used a prior precision of $\delta=0.0008$
and the FMNIST experiments used a prior precision of $\delta=0.0013$.
The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activtions.
In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
architecture with two fully connected classification layers and tanh activations.

In contrast to the GP subset implementation in \citet{immer2021improving},
we do not perform scaling of $\delta$ after the neural network has been trained.
Instead, we use the same prior precision that was used during training.
We performeed a grid search over the prior precision for the NN MAP using the validation NLPD.
We then used this prior precision for the GP predictive (NN) with $M=1024$,
GP predictive with $M=1024$, \our (NN) and \our.
We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.

>>>>

In \cref{sec:image} in the main paper, we included experiments on image data sets. For the image-based classification experiments, we include results using both the GP mean prediction and the NN prediction for both \our and the GP subset.
For the neural network training, we used the same set-up as in \cite{immer2021improving},
training the neural network using Adam for $500$ epochs with a batch size of $512$.
The results reported in \cref{tbl:imagesuper} used a learning rate of $10^{-4}$
and we ran each experiment for $5$ seeds.
The MNIST experiments used a prior precision of $\delta=0.0008$
and the FMNIST experiments used a prior precision of $\delta=0.0013$.
The experiments with MNIST  used an MLP with two hidden layers of width 128 and Tanh activations.
In the FMNIST experiments we followed \cite{immer2021improving} and used a CNN
architecture with two fully connected classification layers and Tanh activations.

In contrast to the GP subset implementation in \citet{immer2021improving},
we do not perform scaling of $\delta$ after the neural network has been trained.
Instead, we use the same prior precision that was used during training.
We performed a grid search over the prior precision for the NN MAP using the validation NLPD.
We then used this prior precision for the GP predictive (NN) with $M=1024$,
GP predictive with $M=1024$, \our (NN) and \our.
We found the MNIST and FMNIST experiments to be numerically stable, even when not performing any clipping in computing the Hessian of the log likelihood, or adding jitter before Cholesky decomposition within the \our dual computation.
